---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# secRetstash

<!-- badges: start -->
<!-- badges: end -->

`secRetstash` is a package that holds functions I use to make my R life easier. It is mainly intended for personal use and R experimentation, you are welcome to poke around and install if you find anything useful! Each function's documentation can be reviewed using `?functionName` and additional examples are below. 

## Installation

You can install the package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("burrowsdt/secRetstash")
```
## Brief Examples
Each function is presented here, sorted alphabetically, with a brief example of its purpose.

### `removeExcept`

`removeExcept` empties your global environment of all objects except those specified by the user. Pass the object name as a string.

```{r removeExcept1}
library(secRetstash)
objectA <- c("a", "b", "c")
objectB <- c("d", "e", "f")

removeExcept("objectA")
```

Pass more than one object name as a string to retain multiple objects.

```{r removeExcept2}

objectA <- c("a", "b", "c")
objectB <- c("d", "e", "f")
objectC <- c("g", "h", "i")
objectD <- c("j", "k", "l")

removeExcept(c("objectA", "objectB"))
```
